TBD

### 2016-09-09 paper/paper.tex
resized equation 3
+ macros

\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\lstset{
  mathescape, 
  language={C},
  basicstyle=\small
}
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   
\usepackage{graphicx}
\usepackage{float,subfig}
\usepackage{xspace,framed}
\usepackage{colortbl}
\usepackage{calc}

@@

@@

The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $P(z)$. However, if implementation aspects are considered during verification, this controller becomes unstable. To properly implement $C(z)$, there is a function $FWL[\cdot]:\mathbb{R}^{k+l+2}\rightarrow Q[\mathbb{R}^{k+l+2}]$, which applies FWL effects to the controller $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable real numbers in the chosen implementation format $<k,l>$ ($k$ is the number of bits of the integer part and $l$ is the number of bits of the fractional part).

For this particular example, the actual implementation of $C(z)$ using $<3,16>$ implementation format can be represented by the following z-expression:

\begin{equation}
\label{Eq:running-example-controller-quantized}
C_{q}\left(z\right) := \frac{2.7199859619140625z^2 - 4.1529998779296875z + 1.89599609375}{z^2 - 1.843994140625z + 0.8495941162109375},
\end{equation}

>>>>

\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\lstset{
  mathescape, 
  language={C},
  basicstyle=\small
}
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   
\usepackage{graphicx}
\usepackage{float,subfig}
\usepackage{xspace,framed}
\usepackage{colortbl}
\usepackage{calc}
\usepackage[dvipsnames]{xcolor}

@@

\include{macros}

@@

The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $P(z)$. However, if implementation aspects are considered during verification, this controller becomes unstable. To properly implement $C(z)$, there is a function $FWL[\cdot]:\mathbb{R}^{k+l+2}\rightarrow Q[\mathbb{R}^{k+l+2}]$, which applies FWL effects to the controller $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable real numbers in the chosen implementation format 
\param{k}{l} ($k$ is the number of bits of the integer part and $l$ is the number of bits of the fractional part).

For this particular example, the actual implementation of $C(z)$ using \param{3}{16} implementation format can be represented by the following z-expression:

\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{0.5\textwidth}{!}{
$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2 - 4.1529998779296875z + 1.89599609375}{z^2 - 1.843994140625z + 0.8495941162109375},$
}
\end{equation}
